---
output:
  github_document:
    html_preview: false
params:
  run_examples: true
---

```{r setup, include=FALSE}
# Normal:  rmarkdown::render("README.Rmd")
# Preview: rmarkdown::render("README.Rmd", params = list(run_examples = FALSE))
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", message = FALSE)
options(tibble.print_max = 5, tibble.width = 75)

```

```{r local-server, include=FALSE, eval=params$run_examples}
server <- callr::r_bg(function() {
  Sys.setenv(TOSI_SERVER_TOKEN = "readme"); tosi.server::run_server()
})
knitr::knit_hooks$set(after.knit = function() server$kill_tree())
tosi::tosi_options(url = "http://127.0.0.1:8788", token = "readme")
```

# tosi

TosiData makes open data easy to find and use in research, analysis,
and reporting. The `tosi` R package lets you retrieve data from multiple sources
in a consistent format and refresh your analysis as new figures become available.

- **Data from many sources.** Access Eurostat, OECD, the ECB, FRED, and national statistical offices through the same simple commands.
- **Ready for analysis.** Get consistently formatted tables you can use directly with dplyr, ggplot2, and other R tools.
- **Designed to save time.** Retrieve data quickly using source IDs or URLs, through the same simple interface.
- **Keep your analysis up to date.** Automatically refresh your results, charts, and reports with new data when you rerun your code.
- **High-fidelity data.** Data stays faithful to its source, retaining the labels, metadata, and version information you need to interpret and verify it.

## How it works

`tosi()` is a multipurpose helper for browsing sources, finding tables, and
retrieving data.

### List connectors:

```{r connectors, eval=params$run_examples}
library(tosi)
tosi()
```

### List tables provided by a connector:

```{r browse, eval=params$run_examples}
tosi("eurostat")  # alternatively: tosi_catalog("eurostat")
```

### Retrieve data:

```{r data, eval=params$run_examples}
tosi("eurostat/tps00001") # Alternatively: tosi_data("eurostat/tps00001")
```

### Search for tables:

```{r search, eval=params$run_examples}
tosi("internet use") # Alternatively: tosi_search("internet use")
```

### Inspect a table's version and structure:

```{r table-info, eval=FALSE}
path <- "eurostat/tps00001"
tosi_data_version(path)
tosi_schema(path)
```

## Install

Install the development version from GitHub:

```{r install, eval=FALSE}
# install.packages("pak")
pak::pak("tosidata/tosi")
```

## Configure

TosiData is currently available by invitation. To discuss access for your
organization, contact [contact@tosidata.com](mailto:contact@tosidata.com).

Connect using your service URL and access token:

```{r configure, eval=FALSE}
tosi_options(
  url = "https://service.example.invalid",
  token = "<your-access-token>"
)
```

For additional settings, see `?tosi_options`.

## Learn more

For arguments and result details, see the `tosi()` function reference.
For questions or problems, use the [issue tracker](https://github.com/tosidata/tosi/issues).
